Chord: A Static and Dynamic Program Analysis Framework for Java

### 2010-04-02 main/doc/chord_sysprops.tex

\begin{longtable}{|l|p{0.4in}|p{4.0in}|}
%\caption{TODO} \\
\hline
{\bf Property name} & {\bf Type} & {\bf Description and default value if any} \\
\endfirsthead
\hline
{\bf Property name} & {\bf Type} & {\bf Description and default value if any} \\
\endhead
\hline
\hline
\multicolumn{3}{|l|}{{\bf Chord resource properties}} \\
\verb+chord.main.dir+ & location & \verb+main+ directory in Chord's installation. \\
\hline
\verb+chord.lib.dir+ & location & Directory containing libraries needed by Chord.
\newline Default: \verb+${chord.main.dir}/lib/+ \\
\hline
\verb+chord.main.class.path+ & path & Classpath of Chord.
It includes the path specified by property \verb+chord.java.analysis.path+
to allow running user-defined program analyses.
\newline Default: See \verb+${chord.main.dir}/build.xml+ \\
\hline
\verb+chord.bddbddb.class.path+ & path & Classpath of \verb+bddbddb+.
\newline Default: See \verb+${chord.main.dir}/build.xml+ \\
\hline
\verb+chord.instr.agent.file+ & location &
Shared library implementing Chord instrumentation agent. \\
%\newline Default: \verb+${chord.main.dir}/lib/libchord_instr_agent.so+ \\
\hline
\verb+chord.javadoc.url+ & string & URL of the Javadoc location of program analyses.
It is used when publishing targets (i.e., when property \verb+chord.publish.targets+
is set to true).
\newline Default: \verb+http://chord.stanford.edu/javadoc/+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Chord boot properties}} \\
\hline
\verb+chord.work.dir+ & location & Working directory during Chord's execution.
\newline Default: current working directory \\
\hline
\verb+chord.props.file+ & location & Properties file loaded by \verb+${chord.main.dir}/build.xml+.
Any of the below properties, as well as other user-defined properties to be passed to Chord
(e.g., for user-defined analyses), may be set in this file.  Each relative (instead of absolute)
path element in the value of any property named \verb+chord.<...>.path+ set in this file is
converted to an absolute path element with respect to the directory containing this file.
\newline Default: \verb+${chord.work.dir}/chord.properties+ \\
\hline
\verb+chord.max.heap+ & string & Maximum memory size of JVM running Chord.
\newline Default: \verb+1024m+ \\
\hline 
\verb+chord.max.stack+ & string & Maximum thread stack size of JVM running Chord.
\newline Default: \verb+32m+ \\
\hline
\verb+chord.jvmargs+ & string & Arguments passed to JVM running Chord. \\
%\newline Default: \verb+"-showversion -ea -Xmx${chord.max.heap} -Xss${chord.max.stack}"+ \\
\hline
\verb+chord.bddbddb.max.heap+ & string & Maximum memory size of JVM running bddbddb.
\newline Default: \verb+1024m+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Chord task properties}} \\
\hline
\verb+chord.build.scope+ & bool & Compute analysis scope (i.e., reachable classes and methods)
using algorithm specified by properties \verb+chord.scope.kind+ and \verb+chord.reuse.scope+.
Program scope is computed regardless of the value of this property if another task (e.g., a
program analysis to be run) needs it.
\newline Default: \verb+false+ \\
\hline
\verb+chord.run.analyses+ & string list & List of names of program analyses to be run
in order.
\newline Default: \verb+""+ \\
\hline
\verb+chord.print.rels+ & string list & List of names of program relations whose contents
must be printed to files \verb+${chord.out.dir}/<...>.txt+ where \verb+<...>+ denotes the
relation name. 
\newline Default: \verb+""+ \\
\hline
\verb+chord.publish.targets+ & bool & Publish all targets defined by program analyses in
paths specified by properties \verb+chord.java.analysis.path+ and
\verb+chord.dlog.analysis.path+.
\newline Default: \verb+false+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Basic program properties}} \\
\hline
\verb+chord.main.class+ & class & Fully-qualified name of main class of given program
(e.g., \verb+com.example.Main+). \\
\hline
\verb+chord.class.path+ & path & Classpath of given program. \verb+${sun.boot.class.path}+
is implicitly appended to it.
\newline Default: \verb+${sun.boot.class.path}+ \\
\hline
\verb+chord.src.path+ & path & Java source path of given program.
\newline Default: \verb+""+ \\
\hline
\verb+chord.run.ids+ & string list & List of IDs to identify runs of given program.
\newline Default: \verb+0+ \\
\hline
\verb+chord.args.XXX+ & string & Command-line argument string to be used for given
program in run having ID \verb+XXX+.
\newline Default: \verb+""+ \\
\hline
\verb+chord.runtime.jvmargs+ & string & Arguments to JVM when running given program.
It is used when the program is executed to compute its scope (i.e., when property
\verb+chord.scope.kind+ is set to \verb+dynamic+) as well as when the instrumented
program is executed for dynamic analyses.
\newline Default: \verb+"-ea -Xmx1024m"+ \\ 
\hline
\hline
\multicolumn{3}{|l|}{{\bf Program scope properties}} \\ 
\hline
\verb+chord.scope.kind+ & [\verb+rta+ $|$ \verb+dynamic+] & Algorithm to compute
analysis scope (i.e., reachable classes and methods).  Current choices include
\verb+rta+ (static Rapid Type Analysis) and \verb+dynamic+ (dynamic analysis).
\newline Default: \verb+rta+ \\
\hline
\verb+chord.reuse.scope+ & bool & Treat analysis scope as the classes and methods listed
in files specified by properties \verb+chord.classes.file+ and \verb+chord.methods.file+,
respectively. Property \verb+chord.scope.kind+ is ignored if this property is set to
\verb+true+ and the two files exist.
\newline Default: \verb+false+ \\
\hline
\verb+chord.check.exclude+ & string list & List of prefixes of names of classes and
packages to be excluded by program analyses.
Interpretation of this property is analysis-specific. \\
%\newline Default: \verb+"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."+ \\
\hline
\verb+chord.instr.exclude+ & string list & List of prefixes of names of classes and
packages to be excluded from being instrumented.  Classes in package \verb+java.lang.ref+
are not instrumented regardless of the value of this property. \\
%\newline Default: \verb+"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Program analysis properties}} \\
\hline
\verb+chord.java.analysis.path+ & path & Classpath containing program analyses written
in Java (i.e., \verb+@Chord+-annotated classes).
\newline Default: \verb+${chord.main.dir}/classes/+ \\
\hline
\verb+chord.dlog.analysis.path+ & path & Path of directories containing program analyses
written in Datalog (i.e., \verb+*.datalog+ and \verb+*.dlog+ files).
\newline Default: \verb+${chord.main.dir}/src/dlog/+ \\
\hline
\verb+chord.reuse.rels+ & bool & Construct program relations from BDDs stored on disk
(from a previous run of Chord) whenever possible instead of re-computing them.
\newline Default: \verb+false+ \\
\hline
\verb+chord.publish.results+ & bool & Publish the results of program analyses in HTML.
Interpretation of this property is analysis-specific.
\newline Default: \verb+true+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Program transformation properties}} \\
\hline
\verb+chord.ssa+ & bool & Do SSA transformation for all methods deemed reachable by the
algorithm used to compute analysis scope.
\newline Default: \verb+true+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Chord debug properties}} \\
\hline
\verb+chord.bddbddb.noisy+ & bool & Make bddbddb output debug info when solving Datalog programs.
\newline Default: \verb+false+ \\
\hline
\verb+chord.save.maps+ & bool & Write to file \verb+${chord.bddbddb.work.dir}/<...>.map+
when saving program domain named \verb+<...>+ (useful for debugging Datalog programs using
\verb+debug+ target of \verb+${chord.main.dir}/build.xml+).
\newline Default: \verb+true+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Chord instrumentation properties}} \\
\hline
\verb+chord.trace.pipe+ & bool & Implement the dynamic trace file as a POSIX pipe instead of a regular file.
\newline Default: \verb+true+ \\
\hline
\verb+chord.trace.block.size+ & int & Number of bytes to read/write in a single operation from/to the dynamic trace file.
\newline Default: \verb+4096+ \\
\hline
\verb+chord.runtime.class+ & class & Subclass of \verb+chord.project.Runtime+ used by dynamic program
analyses to handle events generated during an instrumented program's execution.
\newline Default: \verb+chord.project.BufferedRuntime+ \\
\hline
\hline
\multicolumn{3}{|l|}{{\bf Chord output properties}} \\
\hline
\verb+chord.out.dir+ & location & Directory to which Chord dumps all files.
\newline Default: \verb+${chord.work.dir}/chord_output/+ \\
\hline
\verb+chord.out.file+ & loc. & File to redirect standard output stream during Chord's execution.
\newline Default: \verb+${chord.out.dir}/log.txt+ \\
\hline
\verb+chord.err.file+ & loc. & File to redirect standard error stream during Chord's execution.
\newline Default: \verb+${chord.out.dir}/log.txt+ \\
\hline
\verb+chord.classes.file+ & loc. & File from/to which list of classes deemed reachable is read/written.
\newline Default: \verb+${chord.out.dir}/classes.txt+ \\
\hline
\verb+chord.methods.file+ & loc. & File from/to which list of methods deemed reachable is read/written.
\newline Default: \verb+${chord.out.dir}/methods.txt+ \\
\hline
\verb+chord.bddbddb.work.dir+ & loc. & Directory used by bddbddb as its input/output directory.
\newline Default: \verb+${chord.out.dir}/bddbddb/+ \\
\hline
\verb+chord.boot.classes.dir+ & loc. & Directory containing instrumented JDK classes used by given program.
\newline Default: \verb+${chord.out.dir}/boot_classes/+ \\
\hline
\verb+chord.user.classes.dir+ & loc. & Directory containing instrumented non-JDK classes of given program.
\newline Default: \verb+${chord.out.dir}/user_classes/+  \\
\hline
\verb+chord.instr.scheme.file+ & loc. & File specifying kind and format of events in dynamic trace file.
\newline Default: \verb+${chord.out.dir}/scheme.ser+ \\
\hline
\verb+chord.crude.trace.file+ & loc. & Crude dynamic trace file.
\newline Default: \verb+${chord.out.dir}/crude_trace.txt+ \\
\hline
\verb+chord.final.trace.file+ & loc. & Final dynamic trace file.
\newline Default: \verb+${chord.out.dir}/final_trace.txt+ \\
\hline
\end{longtable}

>>>>

\begin{enumerate}
\item
\code{chord.main.dir} \\
{\bf Type:} location \\
{\bf Description:} \code{main/} directory in Chord's installation.

\item
\code{chord.lib.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing libraries needed by Chord. \\
{\bf Default value:} \code{{chord.main.dir}/lib/}

\item
\code{chord.main.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of Chord.  It includes the path specified by property \code{chord.java.analysis.path} to allow running user-defined program analyses. \\
{\bf Default value:} See \code{{chord.main.dir}/build.xml}

\item
\code{chord.bddbddb.class.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath of \code{bddbddb}. \\
{\bf Default value:} See \code{{chord.main.dir}/build.xml}

\item
\code{chord.instr.agent.file} \\
{\bf Type:} location \\
{\bf Description:} Shared library implementing Chord instrumentation agent. \\
{\bf Default value:} \code{{chord.main.dir}/lib/libchord_instr_agent.so}

\item
\code{chord.javadoc.url} \\
{\bf Type:} string \\
{\bf Description:} URL of the Javadoc location of program analyses.  It is used when publishing targets (i.e., when property \code{chord.publish.targets} is set to true). \\
{\bf Default value:} \code{http://chord.stanford.edu/javadoc/}

\item
\code{chord.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Working directory during Chord's execution. \\
{\bf Default value:} current working directory

\item
\code{chord.props.file} \\
{\bf Type:} location \\
{\bf Description:} Properties file loaded by \code{{chord.main.dir}/build.xml}.  Any of the below properties, as well as other user-defined properties to be passed to Chord (e.g., for user-defined analyses), may be set in this file.  Each relative (instead of absolute) path element in the value of any property named \code{chord.<...>.path} set in this file is converted to an absolute path element with respect to the directory containing this file. \\
{\bf Default value:} \code{{chord.work.dir}/chord.properties}

\item
\code{chord.max.heap} \\
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running Chord. \\
{\bf Default value:} \code{1024m}

\item 
\code{chord.max.stack} \\
{\bf Type:} string \\
{\bf Description:} Maximum thread stack size of JVM running Chord. \\
{\bf Default value:} \code{32m}

\item
\code{chord.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments passed to JVM running Chord. \\
{\bf Default value:} \code{"-showversion -ea -Xmx{chord.max.heap} -Xss{chord.max.stack}"}

\item
\code{chord.bddbddb.max.heap} \\
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running \bddbddb. \\
{\bf Default value:} \code{1024m}

\item
\code{chord.build.scope} \\
 bool \\
 Compute analysis scope (i.e., reachable classes and methods)
using algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}.
Program scope is computed regardless of the value of this property if another task (e.g., a
program analysis to be run) needs it.
{\bf Default value:} \code{false} \\

\item
\code{chord.run.analyses} \\
 string list \\
 List of names of program analyses to be run
in order.
{\bf Default value:} \code{""}

\item
\code{chord.print.rels} \\
{\bf Type:} string list \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{{chord.out.dir}/<...>.txt} where \code{<...>} denotes the relation name.  \\
{\bf Default value:} \code{""}

\item
\code{chord.publish.targets} \\
 bool \\
 Publish all targets defined by program analyses in
paths specified by properties \code{chord.java.analysis.path} and
\code{chord.dlog.analysis.path}.
{\bf Default value:} \code{false} \\

\item
\code{chord.main.class} \\
 class \\
 Fully-qualified name of main class of given program
(e.g., \code{com.example.Main}). \\

\item
\code{chord.class.path} \\
{\bf Type:} path \\
 Classpath of given program. \code{{sun.boot.class.path}}
is implicitly appended to it.
{\bf Default value:} \code{{sun.boot.class.path}}

\item
\code{chord.src.path} \\
{\bf Type:} path \\
 Java source path of given program. \\
{\bf Default value:} \code{""}

\item
\code{chord.run.ids} \\
 string list \\
 List of IDs to identify runs of given program.
{\bf Default value:} \code{0}

\item
\code{chord.args.XXX} \\
 string \\
 Command-line argument string to be used for given
program in run having ID \code{XXX}.
{\bf Default value:} \code{""}

\item
\code{chord.runtime.jvmargs} \\
{\bf Type:} string \\
{\bf Description:} Arguments to JVM when running given program.  It is used when the program is executed to compute its scope (i.e., when property \code{chord.scope.kind} is set to \code{dynamic}) as well as when the instrumented program is executed for dynamic analyses. \\
{\bf Default value:} \code{"-ea -Xmx1024m"}

\item
\code{chord.scope.kind} \\
{\bf Type:} [\code{rta} $|$ \code{dynamic}] \\
{\bf Description:} Algorithm to compute analysis scope (i.e., reachable classes and methods).  Current choices include \code{rta} (static Rapid Type Analysis) and \code{dynamic} (dynamic analysis). \\
{\bf Default value:} \code{rta}

\item
\code{chord.reuse.scope} \\
 bool \\
 Treat analysis scope as the classes and methods listed
in files specified by properties \code{chord.classes.file} and \code{chord.methods.file},
respectively. Property \code{chord.scope.kind} is ignored if this property is set to
\code{true} and the two files exist.
{\bf Default value:} \code{false}

\item
\code{chord.check.exclude} \\
 string list \\
 List of prefixes of names of classes and
packages to be excluded by program analyses.
Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."} \\

\item
\code{chord.instr.exclude} \\
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages to be excluded from being instrumented.  Classes in package \code{java.lang.ref} are not instrumented regardless of the value of this property. \\
{\bf Default value:} \code{"java.,sun.,com.sun.,com.ibm.,org.apache.harmony.,joeq.,jwutil."}

\item
\code{chord.java.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Classpath containing program analyses written in Java (i.e., \code{@Chord}-annotated classes). \\
{\bf Default value:} \code{{chord.main.dir}/classes/}

\item
\code{chord.dlog.analysis.path} \\
{\bf Type:} path \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., \code{*.datalog} and \code{*.dlog} files). \\
{\bf Default value:} \code{{chord.main.dir}/src/dlog/}

\item
\code{chord.reuse.rels} \\
 bool \\
 Construct program relations from BDDs stored on disk
(from a previous run of Chord) whenever possible instead of re-computing them.
{\bf Default value:} \code{false} \\
\item
\code{chord.publish.results} \\
 bool \\
 Publish the results of program analyses in HTML.
Interpretation of this property is analysis-specific.
{\bf Default value:} \code{true} \\

\item
\code{chord.ssa} \\
 bool \\
 Do SSA transformation for all methods deemed reachable by the
algorithm used to compute analysis scope.
{\bf Default value:} \code{true} \\

\item
\code{chord.bddbddb.noisy} \\
 bool \\
 Make \bddbddb\ output debug info when solving Datalog programs.
{\bf Default value:} \code{false} \\

\item
\code{chord.save.maps} \\
 bool \\
 Write to file \code{{chord.bddbddb.work.dir}/<...>.map}
when saving program domain named \code{<...>} (useful for debugging Datalog programs using
\code{debug} target of \code{{chord.main.dir}/build.xml}).
{\bf Default value:} \code{true} \\

\item
\code{chord.trace.pipe} \\
 bool \\
 Implement the dynamic trace file as a POSIX pipe instead of a regular file.
{\bf Default value:} \code{true} \\

\item
\code{chord.trace.block.size} \\
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the dynamic trace file.
{\bf Default value:} \code{4096} \\

\item
\code{chord.runtime.class} \\
{\bf Type:} class \\
{\bf Description:} Subclass of \code{chord.project.Runtime} used by dynamic program analyses to handle events generated during an instrumented program's execution. \\
{\bf Default value:} \code{chord.project.BufferedRuntime}

\item
\code{chord.out.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory to which Chord dumps all files. \\
{\bf Default value:} \code{{chord.work.dir}/chord_output/}

\item
\code{chord.out.file} \\
{\bf Type:} location \\
{\bf Description:} File to redirect standard output stream during Chord's execution. \\
{\bf Default value:} \code{{chord.out.dir}/log.txt}

\item
\code{chord.err.file} \\
{\bf Type:} location \\
{\bf Description:} File to redirect standard error stream during Chord's execution. \\
{\bf Default value:} \code{{chord.out.dir}/log.txt}

\item
\code{chord.classes.file} \\
{\bf Type:} location \\
{\bf Description:} File from/to which list of classes deemed reachable is read/written. \\
{\bf Default value:} \code{{chord.out.dir}/classes.txt}

\item
\code{chord.methods.file} \\
{\bf Type:} location \\
{\bf Description:} File from/to which list of methods deemed reachable is read/written. \\
{\bf Default value:} \code{{chord.out.dir}/methods.txt}

\item
\code{chord.bddbddb.work.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory used by \bddbddb\ as its input/output directory. \\
{\bf Default value:} \code{{chord.out.dir}/bddbddb/}

\item
\code{chord.boot.classes.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing instrumented JDK classes used by given program. \\
{\bf Default value:} \code{{chord.out.dir}/boot_classes/}

\item
\code{chord.user.classes.dir} \\
{\bf Type:} location \\
{\bf Description:} Directory containing instrumented non-JDK classes of given program. \\
{\bf Default value:} \code{{chord.out.dir}/user_classes/}

\item
\code{chord.instr.scheme.file} \\
{\bf Type:} location \\
{\bf Description:} File specifying kind and format of events in dynamic trace file. \\
{\bf Default value:} \code{{chord.out.dir}/scheme.ser}

\item
\code{chord.crude.trace.file} \\
{\bf Type:} location \\
{\bf Description:} Crude dynamic trace file. \\
{\bf Default value:} \code{{chord.out.dir}/crude_trace.txt}

\item
\code{chord.final.trace.file} \\
{\bf Type:} location \\
{\bf Description:} Final dynamic trace file. \\
{\bf Default value:} \code{{chord.out.dir}/final_trace.txt}
\end{enumerate}

### 2010-04-02 main/doc/program_setup.tex

\section{Setting up a Java Program for Analysis}
\label{sec:program-setup}

@@

The above structure is typical: the program's Java source files are under \verb+src/+,
its class files are under \verb+classes/+, the source and jar files of the libraries
used by the program are under \verb+lib/src/+ and \verb+lib/jar/+, respectively.

File \verb+chord.properties+ specifies properties to be passed to Chord (alternatively,
these properties may be passed on the command-line, in format \verb+-D<name>=<value>+).
A sample such file for the above program is as follows:

@@

Each relative (instead of absolute) path element in the value of any property
named \verb+chord.<...>.path+ defined in this file is converted to an absolute path element with respect
to the directory containing this file, which in the above case is \verb+example/+.

Section \ref{sec:chord-sysprops} presents an exhaustive
listing of properties recognized by \Chord.
Here, we only describe those defined in the above
sample \verb+chord.properties+ file:

\begin{itemize}
\item
\verb+chord.main.class+ specifies the fully-qualified name of the main class of the
program.
\item
\verb+chord.class.path+ specifies the classpath of the program.
The value of pre-defined property \verb+${sun.boot.class.path}+ is implicitly appended
to it.
\item
\verb+chord.src.path+ specifies the Java source path of the program.
All program analyses in Chord operate on Java bytecode (specified by \verb+chord.class.path+).
The only use of this property is to HTMLize the Java source files of the program so that the
results of program analyses can be reported at the Java source code level.
\item
\verb+chord.run.ids+ specifies a list of IDs to identify runs of the program.
It is used by dynamic program analyses to determine how many times the program must be run.
An additional use of this property is to allow specifying the command-line arguments to use
in the run having ID \verb+XXX+ via property \verb+chord.args.XXX+, as illustrated by
properties \verb+chord.args.0+ and \verb+chord.args.1+ in the above example.
\end{itemize}

To run Chord on the above program, run the following command in Chord's \verb+main/+ directory:

@@

where \verb+<...>+ denotes either the absolute path, or the path relative to Chord's main directory,
of the parent of directory {\tt example/}.
System property \verb+chord.work.dir+ specifies the working directory during Chord's execution.

The above command causes Chord to load the \verb+chord.properties+ file if present.
The location of this file may be specified explicitly via property
\verb+chord.props.file+ on the above command line.
By default, it is \verb+${chord.work.dir}/chord.properties+.

In the above case, the above command does not do much beyond loading the sample \verb+chord.properties+ file.
For Chord to do something interesting, you need to set additional properties, either
on the above command line or in the \verb+chord.properties+ file, specifying the task(s)
Chord must perform.
All tasks are summarized in the ``Chord task properties" portion of the table in Section \ref{sec:chord-sysprops}.
The two most common tasks, described next, are building program scope (Section \ref{sec:building-scope})
and running program analyses (Section \ref{sec:running-analysis}).

>>>>

\section{Setting up a Java Program}
\label{sec:program-setup}

@@

\noindent The above structure is typical: the program's Java source files are under \code{src/},
its class files are under \code{classes/}, the source and jar files of the libraries
used by the program are under \code{lib/src/} and \code{lib/jar/}, respectively.

File \code{chord.properties} specifies properties to be passed to Chord (alternatively,
these properties may be passed on the command-line, in format \code{-D<name>=<value>}).
A sample such file for the above program is as follows:

@@

Each relative path element in the value of any property
named \code{chord.<...>.path} defined in this file is converted to an absolute path element with respect
to the directory containing this file, which in the above case is \code{example/}.

Section \ref{sec:chord-sysprops} presents an exhaustive
listing of properties recognized by \Chord.
Here, we only describe those defined in the above
sample \code{chord.properties} file:

\begin{itemize}
\item
\code{chord.main.class} specifies the fully-qualified name of the main class of the
program.
\item
\code{chord.class.path} specifies the classpath of the program.
The value of pre-defined property \code{sun.boot.class.path} is implicitly appended
to it.
\item
\code{chord.src.path} specifies the Java source path of the program.
All program analyses in Chord operate on Java bytecode (specified by \code{chord.class.path}).
The only use of this property is to HTMLize the Java source files of the program so that the
results of program analyses can be reported at the Java source code level.
\item
\code{chord.run.ids} specifies a list of IDs to identify runs of the program.
It is used by dynamic program analyses to determine how many times the program must be run.
An additional use of this property is to allow specifying the command-line arguments to use
in the run having ID \code{<id>} via property \code{chord.args.<id>}, as illustrated by
properties \code{chord.args.0} and \code{chord.args.1} in the above example.
\end{itemize}

To run Chord on the above program, run the following command in Chord's \code{main/} directory:

@@

\noindent where \code{<...>} denotes either the absolute path, or the path relative to Chord's \code{main/} directory,
of the parent of directory {\tt example/}.
System property \code{chord.work.dir} specifies the working directory during Chord's execution.

The above command causes Chord to load the \code{chord.properties} file if present.
The location of this file may be specified explicitly via property
\code{chord.props.file} on the above command line.
By default, it is \code{[chord.work.dir]/chord.properties}.

In the above case, Chord does not do much beyond loading the sample \code{chord.properties} file.
For Chord to do something interesting, you need to set additional properties, either
on the above command line or in the \code{chord.properties} file, specifying the task(s)
Chord must perform.
%All tasks are summarized in the ``Chord task properties" portion of the table in Section \ref{sec:chord-sysprops}.
The two most common tasks, described next, are building program scope (Section \ref{sec:building-scope})
and running program analyses (Section \ref{sec:running-analysis}).
